tstrait: a quantitative trait simulator for ancestral recombination graphs

### 2023-11-07 paper.tex
Pass through abstract

\abstract{
\textbf{Summary:}
\texttt{tstrait} is a new open-source Python library that incorporates a wide
range of state-of-the-art algorithms for simulating quantitative traits based
on an ancestral recombination graph (ARG). ARG is an active field of research
in population genetics and statistical genetics due to its promising aspects in
genome-wide association study (GWAS), and this package serves as an essential
infrastructure for utilizing ARG in GWAS simulations. In this work, we provide
an overview of the simulation framework that is incorporated in
\texttt{tstrait} and highlight some recent developments in ARG.\\
\textbf{Availability and Implementation:} \texttt{tstrait} is available as an
open-source Python package. The full documentation with examples and workflow
templates is available on \url{https://tskit.dev/tstrait/docs/}, and the
development version is maintained on Github
(\url{https://github.com/tskit-dev/tstrait}).\\ \textbf{Contact:}
\href{daiki.tagami@hertford.ox.ac.uk}{daiki.tagami@hertford.ox.ac.uk}\\
}

>>>>

\abstract{
\textbf{Summary:}
Ancestral recombination graphs (ARGs) encode the entire ensemble of correlated
genealogical trees arising from recombination in a compact and efficient
structure, and are of fundamental importance in population and statistical
genetics. Recent breakthroughs have made it possible to simulate and
infer ARGs at the population scale, and there is now intense interest
in applying ARG-based methods across a broad range of applications.
Genome-wide association studies (GWAS) are one of the most imporant
application areas, with ARG-based methods already providing substantial
improvements over the state-of-the-art. The ability to efficiently
simulate quantitative traits is critical to developing
and evaluating new GWAS methods, but existing simulators do not scale
to modern datasets and cannot be directly applied to inferred or simulated ARGs.
We present the \texttt{tstrait} package,
an open-source Python library to simulate
quantitative traits on ARGs, and show how this user-friendly software
can be easily applied to vast, population-scale datasets.
\\\textbf{Availability and Implementation:} \texttt{tstrait} is available
for download on the Python Package Index.
Full documentation with examples and workflow
templates is available on \url{https://tskit.dev/tstrait/docs/}, and the
development version is maintained on Github
(\url{https://github.com/tskit-dev/tstrait}).\\ \textbf{Contact:}
\href{daiki.tagami@hertford.ox.ac.uk}{daiki.tagami@hertford.ox.ac.uk}\\
}
